\begin{appendix}
\section{Misc. notes}
We have demonstrated that implementations of INCL and ABLA models in Geant4 provide
an reasonable description of spallation reactions in the 200 MeV - 3 GeV incident energy range 
and that neutron cross sections are reproduced in most cases accurately.



Limitations of INCL model:
\begin{itemize}
\item Energy range: 200 MeV - 3 GeV
\item Projectiles: Protons, Neutrons, Pions, Deuterons, Tritons, He3, Alphas
\item Targets: from Aluminum (maybe even Carbon) up to Uranium
\end{itemize}

Future improvements of INCL model include:
\begin{itemize}
\item Light target handling (including the use of Geant4 Fermi break-up)
\item Light ion projectiles (up to Carbon or even Oxygen)
\end{itemize}


A remodelling of INCL code in Geant4 is in progress.  

\subsection{Physics list design}

\subsubsection{Requirements}
Requirements of the spallation users.

List of requirements:
\begin{enumerate}
\item Validation tool: Spallation example application we use for validation purposes.
\item Accurate neutron production
\item Nucleus fragment production
\item ...
\end{enumerate}

\subsubsection{Implementation}
Since INCL/ABLA covers only one part of the energy range and target
materials, it must be complemented by other models. For energies higher
than 3 GeV the options seem to be QGSP, FTF, Bertini and Binary.

For energies lower than, say, 150 MeV probably using PreCompound might
be a good choice.

Hydrogen-1 (proton) targets (and maybe some other light targets as
well) have to be handled by something else than INCL/ABLA.

For documentation, {\tt Doxygen} seems to be the most promising tool.

\subsubsection{Validation}

Validation tools, strategy, datasets, and results.

%The results of the direct measurements of the ::: flux are in good agreement 
%with the results predicted from the ::: model
%calculations made A.B, and C.D (KEK) and other collaborators.

%It shows that   it also shows that



\lstset{ %
language=bash,                % choose the language of the code
basicstyle=\footnotesize,       % the size of the fonts that are used for the code
numbers=left,                   % where to put the line-numbers
numberstyle=\footnotesize,      % the size of the fonts that are used for the line-numbers
stepnumber=2,                   % the step between two line-numbers. 
                                %If it's 1 each line will be numbered
numbersep=5pt,                  % how far the line-numbers are from the code
showspaces=false,               % show spaces adding particular underscores
showstringspaces=false,         % underline spaces within strings
showtabs=false,                 % show tabs within strings adding particular underscores
frame=single,                   % adds a frame around the code
tabsize=2,                      % sets default tabsize to 2 spaces
captionpos=t,                   % sets the caption-position to bottom
breaklines=true,                % sets automatic line breaking
breakatwhitespace=false,        % sets if automatic breaks should only happen at whitespace
escapeinside={\%*}{*)},          % if you want to add a comment within your code
%caption=Bash function to release a directory., 
label=listing:relRef
}

\end{appendix}
